### 2012-03-20 intention motor representation with corrado sinigaglia/conf spp submit/intention and motor representation SPP submit.tex
before lyon

%a4paper or letterpaper (also used in preamble_steve_paper2
\def \papersize {a4paper}

@@

\def \ititle {Shared Intention and Social Aspects of Motor Representation, or How to Avoid Exoticism}
\def \isubtitle {}
\def \iauthor {
S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano
}
\def \iemail{s.butterfill@warwick.ac.uk}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
%\author{}
%\date{}

@@

\begin{abstract}
\noindent
Are there distinctive roles for shared intention and social motor representation in explaining the purposiveness of joint action?  This question needs some background.  A joint action is a purposive action, or something resembling one, comprising two or more agents' actions.  What is the relation between a joint action and the outcome (or outcomes) to which it is directed?  Standard answers to this question appeal to a notion of shared intention and ignore social motor representation.  It is tempting (for some philosophers, at least) to suppose that social motor representations are only enabling conditions for joint action, or else to suppose that social motor representation is merely a variety of shared intention.  The talk will provide reasons for rejecting both suppositions.  The truth may be that shared intention and social motor representation have distinctive roles in explaining the purposiveness of joint action.  This gives rise to a challenge.  On one hand, effective joint action---imagine erecting a tent in a gale together---sometimes requires both shared intentions and social motor representations plus a certain kind of harmony between the two.  On the other hand, recognizing their distinctive roles precludes the existence of direct inferential links between shared intentions and social motor representations.  The challenge is to explain how these two kinds of representation could sometimes harmoniously contribute to effective joint action despite the lack of inferential integration.

@@

A purposive joint action is an event involving two or more agents' actions where the actions are collectively directed to some outcome.
What is the relation between a joint action and the outcome or outcomes to which it is directed? 
The standard way of answering this question appeals to shared intention,
a structure of states which stands to joint action roughly as an ordinary, individual intention stands to an ordinary, individual action.  
On the standard view, a joint action is directed to an outcome in virtue of the joint action's being appropriately related to a shared intention which represents this outcome or some related outcome. 
As this view is usually expounded, the relation between joint actions and outcomes to which they are directed is treated as largely independent of the motor processes and representations underpinning action execution. 
Motor representations are usually considered either as philosophically irrelevant enabling conditions, or else as merely filling in additional details of the basic schema provided by the standard story. 
Our aim is to show that this is a mistake:
the standard view must be  refined and extended  to accommodate distinctive roles for intention and motor representation in explaining the purposiveness of joint action.

@@

To this end  consider how information about action outcomes is relevant in motor planning, a functional role of motor representation.  Motor planning involves satisfying a variety of requirements. For example, in grasping a mug it is necessary for the hand to prefigure the shape of the mug, to move towards it avoiding potential obstacles and to reach it at a velocity that is both compatible with achieving the type of grip to be used and also suitable given features of the mug such as its fragility and weight \citep{Jeannerod:1995bb,jeannerod:1998nbo}. The need to plan sequences of actions, which may overlap, imposes further requirements. How one should reach for and then grasp a heavy frying pan (say) depends on what one will then do with it. One way of grasping it might be ideal for safely transporting its contents, another for emptying it. 
Requirements on motor planning could not normally be met by explicit practical reasoning, especially given the rapid and fluid transitions involved in many action sequences. 
Rather they require motor processes and representations.
Since 
many of the requirements to be satisfied by motor planning
are partially dependent on action outcomes and not only on  narrowly kinematic or dynamic features of action,
it would be advantageous for some  motor representations to represent action outcomes. 
Given that, as we saw, markers of motor processes carry information about action outcomes, it is now reasonable to conclude that some motor representations are representations of action outcomes.

>>>>

%a4paper or letterpaper (also used in preamble_steve_paper2
\def \papersize {letterpaper}

@@

\def \ititle {Intention and motor representation:}
\def \isubtitle {how to resist temptation}
\def \iauthor {
%S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano
}
\def \iemail{
%	s.butterfill@warwick.ac.uk
}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
\author{}
\date{}

@@

\begin{abstract}
\noindent
Are there distinctive roles for intention and motor representation in explaining the purposiveness of action? Standard philosophical accounts of action assign a role to intention but are silent on motor representation. The temptation is to suppose that nothing need be said here because motor representation is either only an enabling condition for purposive action or else merely a variety of intention. Drawing on cognitive and neuroscientific research, this talk identifies reasons for resisting temptation. Some motor representations, like intentions, coordinate actions in virtue of representing outcomes; but, unlike intentions, motor representations cannot feature as premises or conclusions in practical reasoning.  This implies that motor representation has a distinctive role in explaining the purposiveness of action. It also gives rise to a problem: were the roles of intention and motor representation entirely independent, this would impair effective action. Resisting temptation therefore requires explaining how intentions interlock with motor representations. The solution, we argue, is to recognise that the contents of intention can be partially determined by the contents of motor representations. Understanding this content-determining relation enables better understanding how intention is related to action.

\

\noindent
Word count: 3731 including notes, excluding references

@@

What is the relation between a purposive action and the outcome or outcomes to which it is directed? The standard way of answering this question appeals to intention, a propositional attitude which plays a characteristic role in planning and coordinating action, is linked to practical reasoning and is subject to characteristic norms (\citealp{Bratman:1987xw}).  On the standard view, an action is directed to an outcome in virtue of the action's being appropriately related to an intention which represents this outcome or some related outcome. As this view is usually expounded, the relation between actions and outcomes to which they are directed is treated as largely independent of the motor processes and representations underpinning action execution. Motor representations are usually considered either as philosophically irrelevant enabling conditions, or else as merely filling in additional details of the basic schema provided by the standard story. Our aim is to show that this is a mistake:
the standard view must be  refined and extended  to accommodate distinctive roles for intention and motor representation in explaining the purposiveness of action.

@@

To this end  consider how information about action outcomes is relevant in motor planning, a functional role of motor representation.  Motor planning involves satisfying a variety of requirements. For example, in grasping a mug it is necessary for the hand to prefigure the shape of the mug, to move towards it avoiding potential obstacles and to reach it at a velocity that is both compatible with achieving the type of grip to be used and also suitable given features of the mug such as its fragility and weight \citep{Jeannerod:1995bb,jeannerod:1998nbo}. The need to plan sequences of actions, which may overlap, imposes further requirements. How one should reach for and then grasp a heavy frying pan (say) depends on what one will then do with it. One way of grasping it might be ideal for safely transporting its contents, another for emptying it. 
Requirements on motor planning could not normally be met by explicit practical reasoning, especially given the rapid and fluid transitions involved in many action sequences. 
Rather they require motor processes and representations.
Since 
many of the requirements to be satisfied by motor planning
are partially dependent on action outcomes and not only on  narrowly kinematic or dynamic features of action,
it would be advantageous for some  motor representations to represent action outcomes . 
Given that, as we saw, markers of motor processes carry information about action outcomes, it is now reasonable to conclude that some motor representations are representations of action outcomes.
